Motorcycle Acceleration example

### 2018-11-07 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")
Revised setup instructions for a couple .Rmd files.

An illustration of "smoothing via adaptive shrinkage" (SMASH) applied
to chromatin immunoprecipitation sequencing ("ChIP-seq") data. This
implements the SMASH analysis presented in Sec. 5.2 of the manuscript.

@@

>>>>

This is an illustration of "SMoothing by Adaptive SHrinkage" (SMASH)
applied to chromatin immunoprecipitation sequencing ("ChIP-seq")
data. This implements the SMASH analysis presented in Sec. 5.2 of the
manuscript.

@@

Initial setup instructions
--------------------------

To run this example on your own computer, please follow these setup
instructions. These instructions assume you already have R (optionally,
RStudio) installed on your computer.

Download or clone the [git repository][smash-github] on your computer.

Launch R, and change the working directory to be the "analysis" folder
inside your local copy of the git repository.

Install the devtools, ggplot2 and cowplot packages used here and in
the code below:

```{r install-pkgs-1, eval=FALSE}
install.packages(c("devtools","ggplot2","cowplot"))
```

### 2018-11-07 analysis/motorcycle.Rmd
Revised setup instructions for a couple .Rmd files.

Finally, install the ashr and smashr packages from GitHub:

```{r install-pkgs-2, eval=FALSE}
library(devtools)
install_github("stephens999/ashr",upgrade_dependencies = FALSE)
install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
```

>>>>

Finally, install the smashr package from GitHub:

```{r install-pkgs-2, eval=FALSE}
devtools::install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
```
